Pillar 2 - Topic Modeling

### 2019-01-31 Pillar 2 - Topic Modeling.Rmd
minor editing

# Setup
```{r import data}
load("data_pillar_2.RDATA")
```

@@

```{r compute_tf_idf, cache = TRUE}
compute_tf_idf <- function(data) data %>%
                                   count(`Course ID`, word) %>%
                                   bind_tf_idf(term = word, document = `Course ID`, n = n)

tf_idf_description <- compute_tf_idf(filter(d_description, `Academic Year` == "2018-2019"))
tf_idf_overview    <- compute_tf_idf(filter(d_overview, `Academic Year` == "2018-2019"))
tf_idf_manual      <- compute_tf_idf(d_manual)

@@

  # Barplot
  g <- data %>%
    ggplot(aes(reorder_within(word, tf_idf, facet), tf_idf)) +
    geom_col(show.legend = F) +
    labs(x = NULL, y = "tf-idf") +
    scale_x_reordered() +
    facet_wrap(~ facet, scales = "free", ncol = n_col) +
    coord_flip()

  ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Plots/tf_idf", width = 16, height = 8)

  # Word Cloud
  g <- data %>%
    group_by(facet) %>%
      mutate(freq = tf_idf / sum(tf_idf)) %>% # normalization within clusters
    ggplot(aes(size = freq^0.7, label = word, color = freq^0.7)) +
    geom_text_wordcloud_area(area_corr_power = 1,
                             eccentricity    = 1,
                             rm_outside      = T) +
    scale_radius(range = c(2, 10), limits = c(0, NA)) +
    scale_color_gradient(low = "red", high = "blue") +
    facet_wrap(~ facet, ncol = n_col) + 
    theme(
      strip.text.x     = element_text(),
      panel.background = element_rect(fill = "white"),
      plot.title       = element_text(hjust=0.5)
    )

  ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Plots/tf_idf", width = 16, height = 8)

@@

## Course Level
```{r tf-idf course, cache = TRUE}
prepare_tf_idf_course <- function(data) data %>%
                                          filter(`Course ID` %in% sample(unique(.$`Course ID`), size = 25, replace = F)) %>% # random selection of courses
                                          rename(facet = `Course ID`) %>%
                                          group_by(facet) %>%
                                            filter(n >= 2) %>%
                                            top_n(10, tf_idf) %>%
                                          ungroup

@@

## Cluster Level
```{r tf-idf cluster, cache = TRUE}
prepare_tf_idf_cluster <- function(data) data %>%
                                           left_join(select(d_course, `Course ID`, Cluster), by = "Course ID") %>%
                                           filter(!is.na(Cluster)) %>%
                                           rename(facet = Cluster) %>%
                                           group_by(facet, word) %>%
                                             summarise(tf_idf = sum(tf_idf),
                                                       n = sum(n)) %>%
                                             filter(n >= 10) %>%
                                             top_n(10, tf_idf) %>%
                                           ungroup

@@

## Concentration Level
```{r tf-idf concentration, cache = TRUE}
prepare_tf_idf_concentration <- function(data) data %>%
                                                 left_join(select(d_course, `Course ID`, Concentration, `Concentration (additional)`), by = "Course ID") %>%
                                                 filter(!is.na(Concentration)) %>%
                                                 gather(X, Concentration, Concentration, `Concentration (additional)`, na.rm = TRUE) %>%
                                                 rename(facet = Concentration) %>%
                                                 group_by(facet, word) %>%
                                                   summarise(tf_idf = sum(tf_idf),
                                                             n = sum(n)) %>%
                                                   filter(n >= 10) %>%
                                                   top_n(10, tf_idf) %>%
                                                 ungroup

>>>>

# Setup
```{r import data}
load("output/data_pillar_2.RDATA")

# Only keep course descriptions and overviews from most recent year
d_description <- d_description %>%
  filter(
    `Academic Year` == "2018-2019"
  )

d_overview <- d_overview %>%
  filter(
    `Academic Year` == "2018-2019"
  )
```

@@

```{r compute_tf_idf, cache = TRUE}
compute_tf_idf <- function(data){

  data %>%
    count(
      `Course ID`,
      word
      ) %>%
    bind_tf_idf(
      term = word, 
      document = `Course ID`,
      n = n
      )

tf_idf_description <- compute_tf_idf(d_description)
tf_idf_overview    <- compute_tf_idf(d_overview)
tf_idf_manual      <- compute_tf_idf(d_manual)

@@

  #
  # Barplot
  g <- data %>%
    ggplot(
      aes(
        x = reorder_within(word, tf_idf, facet), 
        y = tf_idf
        )
      ) +
    geom_col(
      show.legend = FALSE
      ) +
    labs(
      x = NULL,
      y = "tf-idf"
      ) +
    scale_x_reordered() +
    facet_wrap(
      facets = ~ facet, 
      scales = "free",
      ncol = n_col
      ) +
    coord_flip()

  ggsave(paste(id_plot, "_BP.jpeg", sep = ""), path = "Output/Plots/tf_idf", width = 16, height = 8)

  #
  # Word Cloud
  g <- data %>%
    group_by(
      facet
      ) %>%
    mutate(
      freq = tf_idf / sum(tf_idf)
      ) %>% # normalization within facet
    ggplot(
      aes(
        size = freq ^ 0.7, 
        label = word, 
        color = freq ^ 0.7
        )
      ) +
    geom_text_wordcloud_area(
      area_corr_power = 1,
      eccentricity    = 1,
      rm_outside      = T
      ) +
    scale_radius(
      range = c(2, 10),
      limits = c(0, NA)
      ) +
    scale_color_gradient(
      low = "red", 
      high = "blue"
      ) +
    facet_wrap(
      facet = ~ facet,
      ncol = n_col
      ) + 
    theme(
      strip.text.x     = element_text(),
      panel.background = element_rect(fill = "white"),
      plot.title       = element_text(hjust = 0.5)
    )

  ggsave(paste(id_plot, "_WC.jpeg", sep = ""), path = "Output/Plots/tf_idf", width = 16, height = 8)

@@

## Course Level
```{r tf-idf course, cache = TRUE}
prepare_tf_idf_course <- function(data){

  data %>%

    # Selection 25 courses randomly
    filter(
      `Course ID` %in% sample(
        x = unique(.$`Course ID`),
        size = 25, 
        replace = FALSE
        )
      ) %>%

    # Select top 10 words per course 
    group_by(
      `Course ID`
      ) %>%
    filter(
      n >= 2
      ) %>%
    top_n(
      n = 10,
      wt = tf_idf
      ) %>%
    ungroup %>%

    # Prepare data for function `plot_tf_idf()`
    rename(
      facet = `Course ID`
      )

@@

## Cluster Level
```{r tf-idf cluster, cache = TRUE}
prepare_tf_idf_cluster <- function(data){

  data %>%

    # Include the variable Cluster
    left_join(
      select(d_course, `Course ID`, Cluster),
      by = "Course ID"
      ) %>%
    filter(
      !is.na(Cluster)
      ) %>%

    # Select top 10 words per cluster
    group_by(
      Cluster, 
      word
      ) %>%
    summarise(
      tf_idf = sum(tf_idf),
      n = sum(n)
      ) %>%
    filter(
      n >= 10
      ) %>%
    top_n(
      n = 10, 
      wt = tf_idf
      ) %>%
    ungroup %>%

    # Prepare data for function `plot_tf_idf()`
    rename(
      facet = Cluster
      )

@@

## Concentration Level
```{r tf-idf concentration, cache = TRUE}
prepare_tf_idf_concentration <- function(data){

  data %>%

    # Include the variable Concentration
    left_join(
      select(d_course, `Course ID`, Concentration, `Concentration (additional)`),
      by = "Course ID"
      ) %>%
    filter(
      !is.na(Concentration)
      ) %>%
    gather(
      key = X,
      value = Concentration,
      Concentration, `Concentration (additional)`,
      na.rm = TRUE
      ) %>%

    # Select top 10 words per cluster
    group_by(
      Concentration, 
      word
      ) %>%
    summarise(
      tf_idf = sum(tf_idf),
      n = sum(n)
      ) %>%
    filter(
      n >= 10
      ) %>%
    top_n(
      n = 10,
      wt = tf_idf
      ) %>%
    ungroup %>%

    # Prepare data for function `plot_tf_idf()`
    rename(
      facet = Concentration
      )
